% mainfile: ../Refinement.tex
\chapter{Introduction}
\pagestyle{scrheadings}	
\setcounter{page}{0}
\pagenumbering{arabic} 
\label{chp_introduction}
Modeling distributed computing systems exhibit various aspects such as modeling the components of the system and modeling the behavior and communication between the concurrent mobile components. Formal specification techniques for such systems have to be able to describe all these aspects. Unfortunately, a single specification technique that is well suited for all these aspects is not yet available. Instead, one finds techniques that are very good at describing individual aspects of system. This observation has led to research into the combination and semantic integration of specification techniques. In this thesis we research combining the two specification techniques:
\picalc{} and Object-Z.

The \picalc{} is a process algebra originally introduced by Robin Milner, Joachim Parrow, and David Walker in \cite{milner1992calculus}. The central concepts of \picalc{} are communication via channels between different processes, creating new channels, parallel composition, and the mobility of channels, which we will use to model the mobility of components. Tool support comes through the \picalc{} visualizer Stargazer and the bisimulation checker ABC.

Object-Z \cite{smith2000the} is an object-oriented extension of the Z formal specification language. It represents a set-theoretic and predicate language for the specification of data. It extends Z by the addition of language constructs resembling the object-oriented paradigm, most notably, classes to encapsulate a state schema, an initial state schema and operation schemas. The state schema specifies the set of the legal states. The initial state schema specifies the set of the legal initial states. The operation schemas specify the legal ways of moving from one state to another.


The main contribution of this thesis is to develop the combination $\pi$-OZ and to transform it into a \picalc{} process, similarly to the approach for CSP-OZ in \cite{olderog}. $\pi$-OZ is a new combination of formal techniques for the specification of components and their behavior. The basic idea is to use a \picalc{} process to specify the behavior of an Object-Z class. This enables the mobility of Object-Z classes through the use of the state pattern \cite{erichgamma1994}, which is a behavioral software design pattern that allows an object to alter its behavior when its state changes. Syntactically, the $\pi$-OZ specification is divided into an OZ part specifying the data and the possible state transitions, and a $\pi$ part specifying the behavior.  This combination is illustrated by the example of a mobile vending machine and two shops, which alternate their behavior when they connect to the mobile vending machine.

 Transforming the combination $\pi$-OZ into a \picalc{} process enables checking the simulation of mobile processes with data. The transformation gives the combination a \picalc{} semantics. The idea is that this semantics comes from the parallel composition of the $\pi$ part and a $\pi$ process, representing the OZ part transformed syntactically into a \picalc{} process.

 Furthermore, we investigate a failure-model and a success-model for the \picalc{} processes and show their relation to the simulation and point out its limitations.

This thesis is divided into five chapters. Chapter 2 gives an overview of the \picalc{} and Object-Z. Thereby, Dynamic OZ, a new extension of Object-Z is introduced to model mobile components with alternating behavior. Chapter 3 proceeds by transforming OZ class into a \picalc{} process. Subsequently, Chapter 4 introduces the combination $\pi$-OZ and its transformation into the \picalc{}. Chapter 5 introduces the failure and the success refinement of the \picalc{} and their relation to the simulation. Finally, the conclusion in Chapter 6 summarizes our results and presents future directions of our research.

