The state pattern \cite{erichgamma1994} is a behavioral software design pattern, that allows an object to alter its behavior when its state changes. It is similar to the concept of finite-state machines. Changing behavior can be seen as that the object has changed its class. To illustrate the idea imagine that our vending machine \textit{VM} is a mobile vending machine and that it is connected by a wireless link $talk$ to a shop \textit{Shop1}. On signal fading, \textit{Shop1} decides to send the link \textit{talk} to another shop \textit{Shop2} through the link \textit{switch} as shown in \refFig{fig_oz_mobile_vending_machine_and_shops}. \textit{Shop1} and \textit{Shop2} change their behavior after switching. This varying behavior of shop can be handled through using two classes \textit{ActiveShop} and \textit{IdleShop}. A shop changes its class when \textit{switch} occurs:
\begin{itemize}
\item \textit{Shop1} sends \textit{talk} via \textit{switch} and changes its class from \textit{ActiveShop} to \textit{IdleShop} as shown in \refFig{fig_oz_active_idle_shop}.
\item \textit{Shop2} receives \textit{talk} via  \textit{switch} and changes its class from \textit{IdleShop} to \textit{ActiveShop} as shown in \refFig{fig_oz_active_idle_shop}.
\end{itemize}
Notice, when an object changes its class it keeps its state variables and skips the \textit{Init} schema of the new class.
Dynamic \oz{} is based on the Agent-Place model used by MobileOZ described in \cite{Kenji2}. MobileOZ has two
essential entities, agents and places. The main difference in the roles of these entities is that agents can move around the network, while places cannot. Dynamic \oz{} takes another approach by allowing places transferring, as shown in \refFig{fig_oz_mobile_vending_machine_and_shops}, where the link $talk$ can be transferred from $Shop1$ to $Shop2$. In Dynamic \oz{}, mobility is achieved
by attaching a distinguished variable \emph{transferableOperation} for storing names of locations. Location transferring
is mimicked by assigning a new location to that variable.
\input{./images/preliminaries/oz/oz_mobile_vending_machine_and_shops}
\input{./images/preliminaries/oz/oz_active_and_idle_shop}
