% mainfile: ../../Refinement.tex
To understand the operational semantics of \picalc{} we will use  a labelled transition system LTS. Using this LTS we can investigate \picalc{} process evolution. The definition of LTS is adapted from \cite{milner} pages 39\footnote{Transition Rules: LTS for concurrent processes not for \picalc{} processes.}, 91\footnote{Reaction Rules: no labels and no LTS.}, 132\footnote{Commitment Rules: abstractions and concretions are out of this thesis's scope.} with some changes.

\subsubsection{Definition}
\begin{definition}[The LTS of \picalc{}]
\label{def_trans_system}

The labelled transition system $(\procs,\traces)$ of \picalc{} processes over the action set $\actions$ has the process expressions $\procs$ as its states, and its transitions $\traces$ are those which can be inferred from the rules in \refFig{fig_transition_rules}.
The rule REACT is the most important one. It shows the process evolution when a reaction occurs. The reaction requires two complementary transitions $P \transs{\out{x}{\vec{y}}} P'$ and $Q \transs{\inp{x}{\vec{z}}} Q'$, we call them commitments. so the process $P$ takes a commitment to take part in the reaction, and so does $Q$.
\input{./images/transitionsystems/transition_rules}
\end{definition}


An example of using the transition rules of this LTS to infer a transition: Let $P\define\procres{x}{(\procpar{\proccall{A}{x}}{\proccall{B}{x}})}$ where: $\procdef{A}{y}\define{}\out{y}{{}}.\proccall{A'}{y}$ and $\procdef{B}{z}\define{}\inp{z}{{}}.\proccall{B'}{z}$. the process $P$ can do the transition $\procres{x}{(\procpar{\proccall{A}{x}}{\proccall{B}{x}})} \transs{\tau} \procres{x}{(\procpar{\proccall{A'}{x}}{\proccall{B'}{x}})}$, which is a reaction.The inference tree of this transition is shown in \refFig{fig_inference_tree}. Thus, using the LTS we can enumerate sll possible transitions of a \picalc{} process.
\input{./images/inference_tree}


