This chapter studies the syntactic transformation of an \oz{} class into an \picalc{} process. The resulting process is intuitively defined as follow:
\[P_{OZ\_PI} = \sum_{v\_st\in Init}^{} \tau. Q(v\_st,v\_self)\]
\begin{equation*}
\begin{aligned}
Q(v\_st,v\_self) ={} & (\sum_{c\in \text{In}}^{} c(v\_in_{c}) \ +\ \sum_{c\in \text{Out}}^{} \tau.c<v\_out_{c}>)\ . \\
      &  \sum_{v\_st'}^{} \tau.Q(v\_st',v\_self)
\end{aligned}
\end{equation*}
where:
\begin{itemize}
\item $\inA$ the set of all input actions, defined as $\inA\define\set[x\in\names]{\inp{x}{\vec{y}}}$.
\item $\outA$ is the set of all output actions, defined as $\outA\define\set[x\in\names]{\out{x}{\vec{y}}}$.
\item $c$ refers to an operation.
\item $v\_st$ refers to the variables of the current state.
\item $v\_st'$ refers to the variables of the successor state.
\item $v\_self$ refers to the instance reference.
\item $c.v\_in_{c}$ refers to the occurrence of the operation $c$, where $v\_in_{c}$ represents the values of the input parameters of $c$.
\item $c.v\_out_{c}$ refers to the occurrence of the operation $c$, where $v\_out_{c}$ represents the values of the output parameters of $c$.
\end{itemize}

What is the benefit of transforming an \oz{} class into \picalc{} process? The main advantage is that it can be combined, using the
parallel operator, with a second, explicit pi-calculus
process that represents the desired sequencing of the operations
of the OZ class. This will enable us to study the behavior of an entity as will be shown later in the next chapter.

To transform an \oz{} class into a \picalc{} process we need to remember that the \picalc{} has only names and processes, and nothing else. A $name$ in \picalc{} can be seen as a \findex{channel} or a \textit{memory location}. Thus, in this work when we use the word \findex{channel} we refer to a \picalc{} \textit{name}. We need to use the names and processes to represent: value, state variable, state schema, initial state schema and operation schema in \picalc{}.
\section{Mapping values}
\findex[process!value]{}
\label{sec_tra_mapping_values}
\input{chapters/mainpart/transformational_semantics_oz/sections/mapping_values/mapping_values}

\section{Mapping state variables}
\findex[process!state variables]{}
\label{sec_tra_mapping_state_variables}
\input{chapters/mainpart/transformational_semantics_oz/sections/mapping_state_variables/mapping_state_variables}

\section{Mapping operations}
\findex[process!operations]{}
\label{sec_tra_mapping_operation}
\input{chapters/mainpart/transformational_semantics_oz/sections/mapping_operation/mapping_operation}

\section{Mapping data Types}
\findex[process!data Types]{}
\label{sec_tra_mapping_data_types}
\input{chapters/mainpart/transformational_semantics_oz/sections/mapping_data_types/mapping_data_types}

\section{Mapping mathematical operators}
\findex[process!mathematical operators]{}
\label{sec_tra_mapping_mathematical_operations}
\input{chapters/mainpart/transformational_semantics_oz/sections/mapping_mathematical_operations/mapping_mathematical_operations}


\section{Mapping OZ class}
\findex[process!OZ class]{}
\label{sec_tra_mapping_class}
\input{chapters/mainpart/transformational_semantics_oz/sections/mapping_class/mapping_class}

\section{Mapping transferable operation's variable}
\findex[process!transferable operation's variable]{}
\label{sec_tra_mapping_transferable_operation}
\input{chapters/mainpart/transformational_semantics_oz/sections/mapping_transferable_operation/mapping_transferable_operation}

